Adaptive Scheduling of Scientific Workflows\\

### 2024-05-07 main.tex
rel. work edited, needs more work

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
%\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{algorithmicx}
%\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{xspace}
\usepackage{hyperref}
\usepackage{numprint}

@@

    \title{Adaptive Scheduling of Scientific Workflows\\
%{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
%should not be used}
    \thanks{Identify applicable funding agency here. If none, delete this.}
    }

@@

    The algorithm presented by Yao\etal~\cite{yao2022memory} looks similar to our heuristics on the first glance, but the
    model the authors adopt differs from the one assumed in this paper.
    The biggest difference is in the way processor memory is represented.
    Each processor has an own internal memory and all processors share a common external one.
    The internal (local) memory is used to store the task files.
    The external memory is used to store evicted files to make room for the execution of a task on a processor.
    However, this marks the decisive difference to our approach: once the files have been evicted into the communication
    buffer in our approach, they can only be transferred to another processor.
    In~\cite{yao2022memory} however, the same processor can evict files and then take them back.
    This makes the approach not directly comparable with ours.
    Other differences in the model include edge weights in the workflow graph.
    Each edges in~\cite{yao2022memory} has two weights - the size of the files transferred along it,
    and the time of communication along this edge, while we assume a singular weight that represents file size and also
    determines the transfer time (along with the bandwidth).
    The tasks themselves have no memory requirements, but need to hold all their incoming and outgoing files.
    They assume that the {\em minimum} local memory should be bigger than the memory requirement of the largest task.

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
%\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{algorithmicx}
%\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{xspace}
\usepackage{hyperref}
\usepackage{numprint}
\usepackage{todonotes}

@@

    \title{Adaptive Scheduling of Scientific Workflows\\
%{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
%should not be used}
    % \thanks{Identify applicable funding agency here. If none, delete this.}
    }

@@

    The algorithm presented by Yao \etal~\cite{yao2022memory} looks similar to our heuristics on the first glance, but the
    model the authors adopt differs from the one assumed in this paper.
    The biggest difference is in the way processor memory is represented.
    In their model, each processor has an own internal memory and all processors share a common external one.
    The internal (local) memory is used to store the task files.
    The external memory is used to store evicted files to make room for the execution of a task on a processor.
    Yet, and this marks the decisive difference to our approach: once the files have been evicted into the communication
    buffer in our approach, they can only be transferred to another processor.
    In~\cite{yao2022memory}, in turn, the same processor can evict files and then take them back.
    This makes the approach not directly comparable with ours.
    Other differences in the model include edge weights in the workflow graph.
    Each edge in~\cite{yao2022memory} has two weights -- the size of the files transferred along it,
    and the time of communication along this edge, while we assume a single weight that represents file size and also
    determines the transfer time (along with the bandwidth).
    The tasks themselves have no memory requirements, but need to hold all their incoming and outgoing files.
    They assume that the {\em minimum} local memory should be bigger than the memory requirement of the largest task.

\todo[inline]{TBD (HM): Still, wouldn't an empirical comparison make sense from a reviewer's point of view?}
